---
title: "Data Cleaning"
author: "Chengyi Wang"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: spacelab
    toc: no
---

```{r}
library(tidyverse)
library(janitor)
library(readxl)
```

Load excel data
```{r}
df <- read_excel("../data/nasopharyngeal carcinoma/Database_for_High-Risk_Nasopharyngeal_Carcinoma_Treated_with_Chemoradiotherapy_and_Immunotherapy.xlsx")
glimpse(df)
```
quick cleaning
```{r}
df <- df %>% clean_names()

```

fix these variables:
- ITT group: The group to which the patient was randomly assigned (1-Standard therapy group; 2-Camrelizumab group)
- safety set: Whether the patient is included in the safety set (1-Yes; 0-No) ("2-No" in readme, but there's no 2)
- PP set: Whether the patient is included in the Per-Protocol set (1-Yes; 0-No) ("2-No" in readme, but there's no 2)
- Metastasis (Y/N): Whether the patient has had distant metastasis or not (0-No; 1-Yes)
- Survival (Y/N): Whether the patient has died or not (0-No; 1-Yes)
- progression (Y/N): Whether the patient has experienced loco-regional relapse, distant metastasis, or death from any cause or not (0-No; 1-Yes)
- Recurrence (Y/N): Whether the patient has had locoregional relapse or not (0-No; 1-Yes)
- Metastasis (Y/N): Whether the patient has had distant metastasis or not (0-No; 1-Yes)
```{r}
df <- df %>% 
  mutate(across(c(safety_set,pp_set,ebv_clearance_status,survival_y_n,progression_y_n,recurrence_y_n,metastasis_y_n),~case_when(
    . == 1 ~ TRUE,
    . == 0 ~ FALSE
  ))) %>% 
  mutate(across(c(itt_group),~case_when(
    . == 1 ~ "Standard therapy group",
    . == 2 ~ "Camrelizumab group"
  ))) %>%  
  mutate(across(where(is.character), as.factor))
```

```{r}
summary(df)
```
```{r}
write_csv(df,"data/cleaned_data.csv")
```




